\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{Local Adaptive Optimization of Time Step}

### 2013-11-04 report/article.tex
Small changes from Lisbeths correction added

Our 1D mass-spring system consists of a set $V$ of vertices and a set
$S$ of springs. Each vertex $v \in V$ has a specified position $p_v$,
mass $m_v$, force $F_v$ and velocity $u_v$, and each spring $s \in S$
has two endpoints vertices $p_{f,s} \in V$ and $p_{t,s} \in V \setminus
p_{f,s}$, a damping factor $d_s$, a stiffness constant $K_s$ and a rest length
$l_{0,s}$. All these variables and constants combined describe the state
of the mass-spring system at each time $t$ during a simulation. All these
variables are initialized in step 1.

@@

The heuristics can be chosen to fit the domain of the simulation, but we have
chosen to use the number of steps since last update, $n_{last}$, and the ratio
between the current spring length and the spring length at the last update
$r_{last}$. This should force a bound on the maximal number of timesteps
before update as well as force frequent updates when the spring is affected by a
high acceleration in opposite direction of the current velocity/direction of
change. \todo{Explain length ratio thought}. Further details are explained in
section \ref{sec:experiments_atomic}.

>>>>

Our 1D mass-spring system consists of a set $V$ of vertices and a set
$S$ of springs. Each vertex $v \in V$ has a specified position $p_v$,
mass $m_v$, force $F_v$ and velocity $u_v$, and each spring $s \in S$
has two endpoints vertices $p_{f,s} \in V$ and $p_{t,s} \in V \setminus
p_{f,s}$, a damping factor $C_s$, a stiffness constant $K_s$ and a rest length
$l_{0,s}$. All these variables and constants combined describe the state
of the mass-spring system at each time $t$ during a simulation. All these
variables are initialized in step 1.

@@

The heuristics can be chosen to fit the domain of the simulation, but we have
chosen to use the number of steps since last update, $n_{last}$, and the ratio
between the current spring length and the spring length at the last update
$r_{last}$. This should force a bound on the maximal number of timesteps
before update as well as force frequent updates when the spring is affected by a
high acceleration in opposite direction of the current velocity/direction of
change. \todo{Explain length ratio thought} Further details are explained in
section \ref{sec:experiments_atomic}.
